### 2017-05-30 paper.tex
Fix latex typography for captial at end of sentence

Once the lesson is ready for release and has a name,
it should be built
and submitted to DOI supplier with its metadata,
such as lesson name, authors (e.g., contributors) and editors (e.g., maintainers).
Due to the collaborative aspect of the lesson development,
the number of authors and even lessons can grow very fast
and it is worth spending some time on automating this release process.
After the formal publishing,
it is also a good idea to publish the built lesson for direct access by the community,
making it clear which version is displayed and what is its corresponding DOI.

>>>>

Once the lesson is ready for release and has a name,
it should be built
and submitted to DOI supplier with its metadata,
such as lesson name, authors (e.g., contributors) and editors (e.g., maintainers).
Due to the collaborative aspect of the lesson development,
the number of authors and even lessons can grow very fast
and it is worth spending some time on automating this release process.
After the formal publishing,
it is also a good idea to publish the built lesson for direct access by the community,
making it clear which version is displayed and what is its corresponding DOI@.
